SNP phylogeny

### 2023-05-20 episodes/snps-phylogeny.Rmd
Draft of data viz

IQ-TREE chose the TVMe+ASC model. We've discussed the ASC above, read more about the TVMe in the [IQ-TREE manual](http://www.iqtree.org/doc/Substitution-Models).

>>>>

IQ-TREE chose the TVMe+ASC model. We've discussed the ASC above, and you can read more about the TVMe in the [IQ-TREE manual](http://www.iqtree.org/doc/Substitution-Models). In short, it is a mdoel where base frequencies are deemed equal, and all rates estimated independently, except the rates of transversions (A <-> G and C <-> T) are equal.
